### 2016-11-17 intro.tex
Rewrote final intro section

\citet{DallaVecchia2012} showed that the temperature of feedback-heated gas can
ultimately determine its effectiveness in driving outflows and regulating star
formation, even with constant feedback energy.  The self-regulating temperature
of superbubbles suggests that nature has a mechanism for setting
this temperature: thermal evaporation.
\bibliographystyle{mnras}
\bibliography{library}

>>>>

\citet{DallaVecchia2012} showed that the temperature of feedback-heated gas can
ultimately determine its effectiveness in driving outflows and regulating star
formation, even with constant feedback energy.  The self-regulating temperature
of superbubbles suggests that nature has a mechanism for setting
this temperature: thermal evaporation.

\section{This Work and Organization of Chapters}
Numerical modeling of galaxies is a difficult problem, as it involves processes
that take place over scales (both spatial and temporal) that span many orders of
magnitude.  This means that simulations will always be unable to resolve at
least some fraction of the physics taking place within the galaxy.  For this,
carefully designed ``sub-grid'' models are required to include the macroscopic
effects that unresolvable microscopic processes yield.  In this thesis, I
present a new sub-grid model for the feedback from massive stars.  I
use that model to investigate how this feedback can regulate the formation of
stars within galaxies, and finally show how this same
feedback is unneeded to produce galaxies that match the observations of
\citet{McGaugh2016}.  I conclude with a summary of these results,
their implications, and some potential future directions for study.

Chapter 2 presents a new superbubble feedback model, and describes the
implementation of this model in the simulation code {\sc GASOLINE2}.  I show a
series of tests that show the model is robust to resolution changes, insensitive
to magnetic field structure, and able to handle cases involving unresolved ISM
structure.  Finally, I show that simulations of isolated dwarf and Milky Way
like disc galaxies regulate their star formation and drive efficient galactic
outflows with this new feedback model.

Chapter 3 applies the feedback model described in Chapter 2 to a cosmological
simulation of a Milky Way like galaxy.  This allows us to see how galaxies like
the Milky Way assembles itself by regulating the flow of gas into the disc,
ejecting material to prevent the formation of a central stellar bulge and slow
the formation of stars.  We compare this to the same simulation run with the
simpler \citet{Stinson2006} feedback model to reproduce the results of
\citet{Stinson2010}, which used the same initial conditions as this study.  We
show that the overproduction of stars seen by \citet{Stinson2010} was not a
failure of SN feedback in general, but because SN feedback simulated without 
thermal evaporation fail to drive mass-loaded winds at high redshift.  These
winds, we demonstrate, remove the fuel for star formation and bulge growth to
produce a realistic, bulgeless disc galaxy.

Chapter 4 extends the results presented in chapter 3 by simulating an additional
17 cosmological galaxies, reproducing the full sample presented in
\citet{Stinson2010} with updated hydrodynamics and the new feebdack model
described in chapter 2.  This sample spans the peak of the star formation
efficiency found by abundance matching studies like \citet{Moster2013}, and
using it we are able to show that supernovae feedback is unable to regulate
galaxies more massive than the peak halo mass of $10^{12}\;M_\odot$.  By
analyzing the outflow properties of these galaxies, we are able to determine a
global relation between the halo mass (or disc mass) and the outflow mass
loadings.  We show that the decreasing efficiency of SN-driven winds is an
inevitable consequence of the energy budget available from SN alone.

Chapter 5 uses the sample of galaxies developed in the previous chapter to
test whether recent observational results presented in \citet{McGaugh2016}
are consistent with $\Lambda CDM$.  The radial acceleration relation (RAR) seen in
the SPARC sample \citep{Lelli2016} of observed rotationally supported galaxies
shows that the true accelerations within these galaxies is tightly correlated 
with the accelerations due to baryons alone.  We show, using the sample of
galaxies generated in chapter 4, that this relation simply falls out of the
dissipative collapse of baryons in a collisionless dark matter halo.  We also
show that this result is independent of stellar feedback.  Despite the insensitivity
to feedback processes at $z=0$, we show that feedback does result in evolution
of the RAR with redshift, and predict that a different RAR would be observed if
a similar study to \citep{Lelli2016} were done for high-redshift galaxies.

Finally, in chapter 6 we conclude with a discussion of how each of these results
together improve our understanding of supernovae-regulated star formation
in the formation of disc galaxies.  We discuss how the results presented here
fit in with past research and the with the current direction of research in
galaxy evolution theory.  We conclude with a discussion of the future directions
that this research points, and a number of open questions related to it that I
hope to answer in the coming years.

\bibliographystyle{mnras}
\bibliography{library}
